---
title: "Reproducibility example: pumpkins"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
```

## Introduction

Write some text here about what you are doing. Show the code for reading in the `pumpkins.csv` file.

```{r code_block1}
# add some code
```

## Converting weights

Write a **function** to alter the weight in pounds to kg. Demonstrate the code below. Then convert the weight and create **a new** column called `weight_kg`

## A pumpkin plot

Here I want you to plot the relationship between the actual weight and the estimated weight. Both axes have to be in the same units - it is up to you whether it is lbs or kg but remember to write some text explaining this.

**Also** explain what the plot shows and whether there are outliers

## Some pumpkin queries

Which pumpkin is the heaviest? Where was it grown and in what year? Show the code below and make sure you return **only the top hit** - nb. `print(n = 1)` will help here.

## Pumpkins in the US and UK

Filter your dataset to include only pumpkins from the UK and US. The code below is intended as a hint:

```{r code_block2, echo = TRUE, eval = FALSE}
filter(country == "A" | country == "B") 
```

Now draw a `ggplot2` boxplot of the weight distributions in the two countries - which country tends to have heavier pumpkins?



